Catchy Title Goes Here

### 2018-06-20 Paper/paper.tex
updated results section for simulated data

\section{Results \label{sec:Results}}
\subsection{Simulated Data \label{subsec:SimDat}}
Although we have chosen a flexible functional form to represent the force of infection and vaccination hazards, we know that that the true functions present in nature are unlikely to be precisely matched by Weibull distributions. This will necessarily lead to some level of biases in our inferences. To understand these possible biases, we analyze simulated data with known foi, vaccination hazard, and $\gamma$ (vaccine efficacy), and examine the results.

Figure~\ref{fig:simplots} shows the results from this analysis. In the top right panel, we show the injected (dashed lines) and recovered (solid lines) curves for the force of infection and vaccination hazard from simulated data with vaccine efficacy ranging between $\gamma = 0.9$  and $\gamma = 0.6$. The top graph in this panel shows the force of infection, and it is very clear that a Weibull distribution is not a good fit for the true force of infection, which is bimodal.  Because of this, we do not expect to be able to accurately infer the simulation parameters (i.e., $\gamma$). We examine the inferred values for this parameter in the top left panel of this same figure.

@@

This panel shows the posterior distributions and assumed values for $\gamma$ from simulated datasets with four different values of $\gamma$. The top plot is generated by analyzing all three datasets, and the bottom plot using only case and vaccination data. In addition to the assumed values and the posteriors, we also show the prior on $\gamma$ as a yellow line. In the top we see, as expected, that the inferred values for $\gamma$ are systematically biased away from the injected values - they turn out to be consistently biased low in this case. Although this means that we do not necessarily infer an accurate value for vaccine efficacy with this data using this model, it is important to note that we do infer the correct \emph{ordering} for $\gamma$. That is, if these were four different locations, we would correctly identify the location with the lowest vaccine efficacy.

The bottom plot in this same panel shows the inferred values for vaccine efficacy using only case and vaccination data - i.e. leaving out the serology data from the analysis. For the higher levels of $\gamma$, the results are dominated by the prior. For the lower values, the recovered values are again biased quite low, but also again recover the correct ranking of vaccine efficacy.

Finally, we wish to explore the recovered fits to the true data when analyzing all of the simulated datasets. These results are shown in the bottom panel of Fig.~\ref{fig:simplots}. Here, we show the recovered (lines) seroprevalence, vaccination probability, and case distribution for simulated data with vaccine efficacy of $\gamma = 0.6$ (indigo) and $\gamma = 0.9$ (orange). The true values for each of these are shown as points. We can see that the injected data is recovered well with our model, even though the foi and vaccination hazard are not fit particularly well themselves. This is because the data are a function of the \emph{integrated} foi and vaccination hazard, which allows for some ambiguity in the details of the functions themselves.

>>>>

\section{Results \label{sec:Results}}
\subsection{Simulated Data \label{subsec:SimDat}}
%Although we have chosen a flexible functional form to represent the force of infection and vaccination hazards, we know that that the true functions present in nature are unlikely to be precisely matched by Weibull distributions. This will necessarily lead to some level of biases in our inferences. To understand these possible biases, we analyze simulated data with known foi, vaccination hazard, and $\gamma$ (vaccine efficacy), and examine the results.

Using simulated age-specific case data and a simulated vaccine coverage survey, we estimated the cumulative proportion sero-positive as a function of age (Figure~\ref{fig:simplots}) under different scenarios of vaccine effectiveness (see definition above).  Using the model fit without using serology data, the estimated age-specific sero-prevalence was broadly consistent with the simualated sero-prevalence, though with a slight negative bias (Figure~\ref{fig:simplots} a). Similarly, the estimated cumulative probability of vaccination as a function of age was unbiased for the simulated values (Figure~\ref{fig:simplots} b).

The Weibull distribution used to approximate the age-specific FOI is an over-simplification of the complex age-specific mixing represented in the POLYMOD WAIFW matrix used in the MSIRV simulations; and is likely to be an over-simplification of the true, but unknown, age-specific FOI that exists in any real-world epidemiological setting.  Acknowledging that limitation, the estimated Weibull FOI broadly reflects the average age-specific FOI from the MSIRV model(Figure~\ref{fig:simplots} d) ; the latter is calculated as the product of the WAIFW matrix and the average age-specific vector of infectious cases over the full simulation.  The resulting Weibull fit, which is necessarily unimodal, tends to average over the two modes in the simulated FOI which reflect the effect of age-assortative mixing and interactions among generations (i.e. parents and children).  The estimated vaccination hazard clearly identifies the mode of age-specific vaccination and the magnitude of the vaccination hazard is positively correlated with the simulated values (Figure~\ref{fig:simplots} e).

The vaccine effectiveness, $\gamma$, which measures the likelihood that a child recorded as vaccinated in a vaccine survey was immunized by vaccine, is poorly estimated using a model fit only to age-specific case incidence and vaccination survey data (Figure~\ref{fig:simplots} f).  The fitted values of vaccine is positively correlated with the true value used in simulation, but exhibits significant negative bias; in simulation runs with low effectiveness, the resulting posterior estiamte was low and significantly different than the prior on $\gamma$ (Figure~\ref{fig:simplots} f).  This bias is off-set by slight biases in other parameters (see Supplement), which explains why the estimated age-specific sero-prevalence only exhibited a slight negative bias. Estimated vaccine effectiveness remains biased in the correspoding model that includes seroprevalence (Eq 8); though the correlation between the posterior mean estimate and the true value used in simulation is stronger and the variance of the posterior distribution is smaller when serology data are included (Figure~\ref{fig:simplots} g).  Thus, while vaccine effectiveness may always be challenging to estimate, the resulting estimate from this model may serve as an indicator of vaccine effectiveness.  Results for the age-specific sero-prevalence, probabilty of vaccination, and the hazards for FOI and vaccination (e.g. corresponding to (Figure~\ref{fig:simplots}) for the model fit to age-specific case incidence, vaccination survey data, and seroprevalence data are presented in the Supplement.

%Figure~\ref{fig:simplots} shows the results from this analysis. In the top right panel, we show the injected (dashed lines) and recovered (solid lines) curves for the force of infection and vaccination hazard from simulated data with vaccine efficacy ranging between $\gamma = 0.9$  and $\gamma = 0.6$. The top graph in this panel shows the force of infection, and it is very clear that a Weibull distribution is not a good fit for the true force of infection, which is bimodal.  Because of this, we do not expect to be able to accurately infer the simulation parameters (i.e., $\gamma$). We examine the inferred values for this parameter in the top left panel of this same figure.

@@

%This panel shows the posterior distributions and assumed values for $\gamma$ from simulated datasets with four different values of $\gamma$. The top plot is generated by analyzing all three datasets, and the bottom plot using only case and vaccination data. In addition to the assumed values and the posteriors, we also show the prior on $\gamma$ as a yellow line. In the top we see, as expected, that the inferred values for $\gamma$ are systematically biased away from the injected values - they turn out to be consistently biased low in this case. Although this means that we do not necessarily infer an accurate value for vaccine efficacy with this data using this model, it is important to note that we do infer the correct \emph{ordering} for $\gamma$. That is, if these were four different locations, we would correctly identify the location with the lowest vaccine efficacy.

%The bottom plot in this same panel shows the inferred values for vaccine efficacy using only case and vaccination data - i.e. leaving out the serology data from the analysis. For the higher levels of $\gamma$, the results are dominated by the prior. For the lower values, the recovered values are again biased quite low, but also again recover the correct ranking of vaccine efficacy.

%Finally, we wish to explore the recovered fits to the true data when analyzing all of the simulated datasets. These results are shown in the bottom panel of Fig.~\ref{fig:simplots}. Here, we show the recovered (lines) seroprevalence, vaccination probability, and case distribution for simulated data with vaccine efficacy of $\gamma = 0.6$ (indigo) and $\gamma = 0.9$ (orange). The true values for each of these are shown as points. We can see that the injected data is recovered well with our model, even though the foi and vaccination hazard are not fit particularly well themselves. This is because the data are a function of the \emph{integrated} foi and vaccination hazard, which allows for some ambiguity in the details of the functions themselves.
